Slitasje og kjørespor

### 2023-01-02 DRAFT_slitasjeOgKjørespor.Rmd
fix: point to polygon

Fix class

```{r}
naturetypes$kartleggingsår <- as.numeric(naturetypes$kartleggingsår)
naturetypes$area <- units::drop_units(naturetypes$area)
```

@@

The ANO data is point data, and the nature type data is multipolygon.

Grouping and tallying the data for plotting

```{r}
temp <- as.data.frame(table(slitasje_data$slitasje))
```

@@

## Prepare export

@@

<!-- Export final file. Ideally a georeferenced shape or raster wit indicators values (raw and normalised), reference values and errors. -->

>>>>

Fix class
```{r}
naturetypes$kartleggingsår <- as.numeric(naturetypes$kartleggingsår)
naturetypes$area <- units::drop_units(naturetypes$area)
```

@@

The ANO data is point data, and the nature type data is multipolygon. Because later we want to save this as a shape file, we cannot have a mixed class type. I will therefore convert the points to polygons. I use the area column to calculate a radii that gives that area.
```{r}
slitasje_data_points <- slitasje_data %>%
  mutate(g_type = st_geometry_type(.)) %>%
  filter(g_type =="POINT") %>%
  st_buffer(sqrt(slitasje_data$area/pi))
```

Checking no that the new polygons have the area corresponding to the proportion of the point that was part of the same main ecosystem:
```{r new-area, fig.cap="Checking that the area of the new polygons fall in line with the proportion of each point which is part of the main ecosystem."}
slitasje_data_points$area2 <- st_area(slitasje_data_points)
plot(slitasje_data_points$area, slitasje_data_points$area2,
     xlab = "Target area",
     ylab = "Area of the new polygons")
```

The area calculation seems to have worked fine.

```{r}
slitasje_data_polygons <- slitasje_data %>%
  mutate(g_type = st_geometry_type(.)) %>%
  filter(g_type !="POINT")

slitasje_data <- bind_rows(slitasje_data_points, slitasje_data_polygons)

The new dataset only contains polygons.

Grouping and tallying the data for plotting
```{r}
temp <- as.data.frame(table(slitasje_data$slitasje))
```

@@

## Prepare export
According to the workflow spesifications, I will export the indicator map at its highest resolution, but I also need to export a map of the *homogeneous areas* over which I will aggregate the indicator values. For the finest resolution indicator map I will not include columns for uncertainty (because this will only be estimated at the aggregated level), or reference levels (because there is no spatial variation).

```{r}
exp_wetland <- select(slitasje_data[slitasje_data$hovedøkosystem == "Våtmark",],
              origin,
              area,
              i_2020,
              SHAPE
              )

```{r, eval=F}
st_write(exp_wetland, "indicators/indicatorMaps/wetland_slitasje.shp",
         append = F)
```

@@

<!-- Export final file. Ideally a georeferenced shape or raster with indicators values (raw and normalised), reference values and errors. -->
